\section{Summary}
I consider my primary commitment to be in \keyword{thinking} and \keyword{solving problems} well. 
Put another way, as a task of grasping the \keyword{essence} of a given subject clearly 
through a comprehensive view of the subject as both a unified whole and as a composition of relations. 
\mynotes{
Put another way, as a task of grasping the essence of a given subject clearly, 
which requires understanding it comprehensibly as a harmonious whole comprised of a delicate balance of various complex parts and relations, like a beautiful painting. 
The fun is in accomplishing the goal without crippling the balance.

like a beautiful painting.
Nothing is arbitrary.

a coherent whole of complex relations and nothing is arbitrary, like a beautiful painting. 
a clear understanding of both the whole and the parts and the relations bringing them all together.
thinking not only logically but comprehensibly
understanding the whole as a harmonious whole comprised of a delicate balance of various complex parts and relations
no choice is arbitrary but has a clear place in relation to the whole
visualize both the big picture and the deep underlying parts in relation to the whole.
visualize all levels from the big picture at the top down to the deep underlying details in relation to the whole 
across all levels from the big picture and context at the top to the deep inner details.
}
Hence, I do not feel inherently bound to any specific conditions, and have adapted to various roles and environments as necessary.
However, I have always been naturally inclined toward and enjoyed more logically-oriented work, such as \keyword{backend development} and \keyword{system architecting}, 
and would prefer to pursue this path further as much as possible.
% However, I derived much fulfillment from my last 8 year experience as a \keyword{backend developer} and {architect}, 
% and would prefer to pursue this path in greater depth as much as possible.
In particular, it was very fulfilling  
\keyword{designing} core system elements, such as the APIs, data structures, and protocols and 
solving \keyword{distributed systems} problems.
\mynotes{
As such, I do not feel attached too strongly to specific labels, such as specific roles, technologies, and tools, but am content adapting to any environment as necessary. 
Consequently, I strive to not bind myself too strongly to specific labels, such as specific roles, technologies, and tools. 
However, I derived much fulfillment from most recent 8 year experience as a \keyword{backend developer} and \keyword{architect}.
In particular, it was very fulfilling to work on \keyword{distributed systems} problems and \keyword{designing APIs, data structures, and protocols}, 
and I am keen on pursuing this path further as much as possible.
}

\begin{description}
  \liststyle
  \item[Languages]{Bilingual. Fluent in Japanese (first language) and English}
  \item[Personal tools]{\rfneovim /\rfvim, \rfbash (scripting), \rfgit, \rftmux }
  \item[Knowledge library]{https://ynishiza.github.io/notes/}
  \item[Most recent experiences]{\rfnodejs, \rfmongodb, \rfredis, \rfneofj, \rfdocker, \rfreact, \rfcypress  }
  % \item[Main interests]{backend development, software architecting, distributed systems, networks and protocols}
  \item[Interests]{distributed systems, networks and protocols, data structures, algorithms, reading RFCs, \rfhaskell }
  \item[Other]{Enjoys walking, writing, tennis. Grew up in Japan, Canada, Yemen, Qatar.}
\end{description}
